\textbf{Appendix}\\ Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2020-09-02 Chapter_0/04_Manuscript/Manuscript_Support.tex
Working on paper revision
Worked on the revision for BES paper

\documentclass[abstract=off,10pt,a4paper,bibliography=totocnumbered]{article}
\usepackage[paper=a4paper,left=35mm,right=35mm,top=25mm,bottom=30mm]{geometry}
\usepackage[doublespacing]{setspace}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{lineno}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage[flushleft]{threeparttable}

@@

%------------------------------------------------------------------------------
%	Appendix S1: Net Squared Displacement
%------------------------------------------------------------------------------
\section{Net Squared Displacement}
\begin{figure}[hbpt]
  \begin{center}
    \includegraphics[width = \textwidth]{99_NSD.pdf}
    \caption{NSD displacement through time for one of our dispersers. The blue
    line indicates the period during which we calssified the individual as
    dispersing.}
    \label{NSD}
  \end{center}
\end{figure}

@@

\begin{table}[hbtp]
  \caption{Summary statistics of all GPS relocations that have been recorded on
  dispersing coalitions.}
  \label{GPSData}
  \begin{center}
    \resizebox{0.8\textwidth}{!}{
      \begin{tabular}{lccccccc}
      \toprule
      \parbox[]{2cm}{\centering Coalition ID} &
        \parbox[]{1cm}{\centering Sex} &
          \parbox[]{2cm}{\centering \ Pack \\ Affiliation} &
            \parbox[]{1.5cm}{\centering \# Fixes \\ Total} &
              \parbox[]{1.5cm}{\centering \# Fixes \\ During \\ Dispersal} &
                \parbox[]{1.5cm}{\centering \# Days \\ Dispersing} &
                  \parbox[]{2cm}{\centering Euclidean \\ Dispersal\\ Distance \\ (in km)} &
                    \parbox[]{2cm}{\centering Cumulative \\ Dispersal \\ Distance \\ (in km)} \\
      \midrule
      Abel & M & MU & 894 & 45 & 9 & 131 & 205 \\
      Amacuro & F & MB & 954 & 583 & 137 & 23 & 1'090 \\
      Belgium & M & ZU & 1'097 & 158 & 28 & 18 & 319 \\
      Dalwhinnie & F & PA & 545 & 62 & 22 & 50 & 243 \\
      Denali & F & MN & 1'096 & 173 & 33 & 11 & 528 \\
      Everest & M & MN & 389 & 123 & 38 & 67 & 572 \\
      Kalahari & F & HT & 1'753 & 467 & 130 & 20 & 1'963 \\
      Karisimbi & M & MN & 438 & 141 & 34 & 45 & 251 \\
      Liuwa & F & AP & 946 & 92 & 19 & 144 & 451 \\
      Lupe & M & KW & 2'209 & 396 & 34 & 8 & 436 \\
      MadameChing & F & AP & 776 & 729 & 136 & 263 & 1'560 \\
      Mirage & M & HT & 814 & 182 & 36 & 7 & 435 \\
      Odzala & M & AP & 1'410 & 205 & 42 & 53 & 412 \\
      Scorpion & M & KB & 2'676 & 393 & 34 & 4 & 471 \\
      Stetson & M & MT & 384 & 383 & 33 & 3 & 481 \\
      Taryn & F & AP & 896 & 37 & 9 & 10 & 130 \\
      \bottomrule
      \end{tabular}
    }
  \end{center}
\end{table}

%------------------------------------------------------------------------------
%	Appendix S3: Spatial Covariates
%------------------------------------------------------------------------------
\newpage
\section{Spatial Covariates}
To investigate habitat preferences of dispersing wild dogs, we used a set of
geo-referenced covariates that we aggregated in the categories \textit{land
cover}, \textit{protection status}, and \textit{human influence}. We did not
include terrain features as covariates due to the absence of noteworthy
elevational gradients in our study area. For each covariate, we prepared spatial
raster layers from freely available online services or from remotely sensed
satellite imagery. To ensure a consistent resolution (i.e. cell-size or grain)
across covariates, we coarsened or interpolated all layers to match a resolution
of 250m x 250m. We performed processing and manipulation of data as well as all
spatial and statistical analyses using R, version 3.6.1 \citep{R.2019}.

@@

%------------------------------------------------------------------------------
%  Appendix S6: Least Cost Paths and Least Cost Corridors
%------------------------------------------------------------------------------
\newpage
\section{Identification of Least-Cost Paths \& Corridors}
\subsection{Least-Cost Paths}
We implemented factorial LCP analysis between source points using the R-package
\textit{gdistance} (Figure S.7; \citealp{vanEtten.2017}). The package translated
the (unscaled) permeability surface into a network of nodes to find shortest
effective distances between source points based on probabilities of moving from
cell to cell. In our case, the transition probability of moving between two
adjacent cells depended on their averaged permeability. We allowed individuals
to move from each cell to the cell's eight surrounding neighbors (i.e. Moores
neighborhood) and applied a geographic correction to account for the fact that
diagonal neighbors were more remote than orthogonal neighbors. Because African
wild dogs have been observed to cover large dispersal distances
\citep{DaviesMostert.2012, Masenga.2016, Cozzi.2020}, we did not limit LCPs to a
maximal effective cost. After computation, we tallied overlapping LCPs and
identified high-frequency routes.

@@

%  Appendix S7: AIC Model Selection

@@

          cos(ta) + log(sl) + W + T + DTW + HI + S & 90091.40 & 0.00 & 1.00 & -45030.70 \\
          cos(ta) + log(sl) + W + T + DTW + HI + S + DTR & 90093.51 & 2.11 & 0.00 & -45029.75 \\
          cos(ta) + log(sl) + W + T + DTW + HI & 90094.79 & 3.38 & 0.00 & -45034.39 \\
          cos(ta) + log(sl) + W + T + DTW + HI + S + P & 90095.05 & 3.65 & 0.00 & -45030.52 \\
          cos(ta) + log(sl) + W + T + DTW + S & 90096.95 & 5.55 & 0.00 & -45035.47 \\
          cos(ta) + log(sl) + W + T + DTW + HI + DTR & 90097.02 & 5.62 & 0.00 & -45033.51 \\
          cos(ta) + log(sl) + W + T + DTW + HI + S + DTR + P & 90097.38 & 5.98 & 0.00 & -45029.69 \\
          cos(ta) + log(sl) + W + T + DTW + HI + S + RC & 90097.53 & 6.13 & 0.00 & -45029.76 \\
          cos(ta) + log(sl) + W + T + DTW + HI + P & 90098.46 & 7.06 & 0.00 & -45034.23 \\
          cos(ta) + log(sl) + W + T + DTW + HI + S + DTR + RC & 90099.62 & 8.22 & 0.00 & -45028.81 \\
          cos(ta) + log(sl) + W + T + DTW & 90099.97 & 8.57 & 0.00 & -45038.99 \\
          cos(ta) + log(sl) + W + T + DTW + HI + RC & 90100.68 & 9.28 & 0.00 & -45033.34 \\
          cos(ta) + log(sl) + W + T + DTW + DTR & 90101.68 & 10.28 & 0.00 & -45037.84 \\
          cos(ta) + log(sl) + W + T + DTW + P & 90103.07 & 11.67 & 0.00 & -45038.54 \\
          cos(ta) + log(sl) + W + T + DTW + HI + S + DTR + P + RC & 90103.48 & 12.08 & 0.00 & -45028.74 \\
          cos(ta) + log(sl) + W + T + DTW + RC & 90104.72 & 13.32 & 0.00 & -45037.36 \\
          cos(ta) + log(sl) + W + T + HI & 90123.71 & 32.31 & 0.00 & -45050.85 \\
          cos(ta) + log(sl) + W + T & 90128.17 & 36.77 & 0.00 & -45055.09 \\
          cos(ta) + log(sl) + W + T + S & 90129.36 & 37.96 & 0.00 & -45053.68 \\
          cos(ta) + log(sl) + W + T + DTR & 90130.11 & 38.71 & 0.00 & -45054.05 \\
          cos(ta) + log(sl) + W + T + P & 90131.75 & 40.35 & 0.00 & -45054.88 \\
          cos(ta) + log(sl) + W + T + RC & 90133.53 & 42.13 & 0.00 & -45053.77 \\
          cos(ta) + log(sl) + W + DTW & 90138.92 & 47.52 & 0.00 & -45060.46 \\
          cos(ta) + log(sl) + W + HI & 90149.30 & 57.90 & 0.00 & -45065.65 \\
          cos(ta) + log(sl) + W + S & 90151.14 & 59.74 & 0.00 & -45066.57 \\
          cos(ta) + log(sl) + W & 90153.70 & 62.30 & 0.00 & -45069.85 \\
          cos(ta) + log(sl) + W + DTR & 90156.32 & 64.92 & 0.00 & -45069.16 \\
          cos(ta) + log(sl) + W + P & 90157.23 & 65.83 & 0.00 & -45069.62 \\
          cos(ta) + log(sl) + W + RC & 90159.32 & 67.91 & 0.00 & -45068.66 \\
          cos(ta) + log(sl) + S & 90161.07 & 69.67 & 0.00 & -45073.54 \\
          cos(ta) + log(sl) + DTW & 90262.03 & 170.63 & 0.00 & -45124.01 \\
          cos(ta) + log(sl) + T & 90301.56 & 210.16 & 0.00 & -45143.78 \\
          cos(ta) + log(sl) + HI & 90307.55 & 216.15 & 0.00 & -45146.78 \\
          cos(ta) + log(sl) + DTR & 90316.37 & 224.97 & 0.00 & -45151.19 \\
          cos(ta) + log(sl) + P & 90316.62 & 225.22 & 0.00 & -45151.31 \\
          cos(ta) + log(sl) + RC & 90318.46 & 227.06 & 0.00 & -45150.23 \\

@@

         Road Crossing, DTR = Distance To Roads.

>>>>

\documentclass[abstract=off,10pt,a4paper,bibliography=totocnumbered]{article}
\usepackage[paper=a4paper,left=35mm,right=35mm,top=25mm,bottom=30mm]{geometry}
\usepackage[doublespacing]{setspace}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{lineno}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage[flushleft]{threeparttable}
\usepackage{todonotes}

@@

%------------------------------------------------------------------------------
%	Appendix S1: Net Squared Displacement
%------------------------------------------------------------------------------
\section{Net Squared Displacement}\todo{Reviewer 1 pointed out that we need to
replace calssified with classified}
\begin{figure}[hbpt]
  \begin{center}
    \includegraphics[width = \textwidth]{99_NSD.pdf}
    \caption{NSD displacement through time for one of our dispersers. The blue
    line indicates the period during which we classified the individual as
    dispersing.}
    \label{NSD}
  \end{center}
\end{figure}

@@

\begin{table}[hbtp]
  \caption{Summary statistics of all GPS relocations that have been recorded on
  dispersing coalitions.}
  \label{GPSData}
  \begin{center}
    \resizebox{0.8\textwidth}{!}{
      \begin{tabular}{lccccccc}
      \toprule
      \parbox[]{2cm}{\centering Coalition ID} &
        \parbox[]{1cm}{\centering Sex} &
          \parbox[]{2cm}{\centering \ Pack \\ Affiliation} &
            \parbox[]{1.5cm}{\centering \# Fixes \\ Total} &
              \parbox[]{1.5cm}{\centering \# Fixes \\ During \\ Dispersal} &
                \parbox[]{1.5cm}{\centering \# Days \\ Dispersing} &
                  \parbox[]{2cm}{\centering Euclidean \\ Dispersal\\ Distance \\ (in km)} &
                    \parbox[]{2cm}{\centering Cumulative \\ Dispersal \\ Distance \\ (in km)} \\
      \midrule
      Abel & M & MU & 894 & 45 & 9 & 131 & 205 \\
      Amacuro & F & MB & 954 & 583 & 137 & 23 & 1'090 \\
      Belgium & M & ZU & 1'097 & 158 & 28 & 18 & 319 \\
      Dalwhinnie & F & PA & 545 & 62 & 22 & 50 & 243 \\
      Denali & F & MN & 1'096 & 173 & 33 & 11 & 528 \\
      Everest & M & MN & 389 & 123 & 38 & 67 & 572 \\
      Kalahari & F & HT & 1'753 & 467 & 130 & 20 & 1'963 \\
      Karisimbi & M & MN & 438 & 141 & 34 & 45 & 251 \\
      Liuwa & F & AP & 946 & 92 & 19 & 144 & 451 \\
      Lupe & M & KW & 2'209 & 396 & 34 & 8 & 436 \\
      MadameChing & F & AP & 776 & 729 & 136 & 263 & 1'560 \\
      Mirage & M & HT & 814 & 182 & 36 & 7 & 435 \\
      Odzala & M & AP & 1'410 & 205 & 42 & 53 & 412 \\
      Scorpion & M & KB & 2'676 & 393 & 34 & 4 & 471 \\
      Stetson & M & MT & 384 & 383 & 33 & 3 & 481 \\
      Taryn & F & AP & 896 & 37 & 9 & 10 & 130 \\
      \toprule
      \toprule
      \textit{Mean} & - & - & 1080 & 261 & 48 & 54 & 597 \\
      \textit{(SD)} & - & - & (649) & (207) & (44) & (71) & (508) \\
      \bottomrule
      \end{tabular}
    }
  \end{center}
\end{table}

%------------------------------------------------------------------------------
%	Appendix S3: Spatial Covariates
%------------------------------------------------------------------------------
\newpage
\section{Spatial Covariates}
To investigate habitat preferences of dispersing wild dogs, we used a set of
geo-referenced covariates that we aggregated in the categories \textit{land
cover}, \textit{protection status}, and \textit{human influence}. We did not
include any terrain features due to the absence of noteworthy elevational
gradients in our study area. For each covariate, we prepared spatial raster
layers from freely available online services or from remotely sensed satellite
imagery. To ensure a consistent resolution (i.e. cell-size or grain) across
covariates, we coarsened or interpolated all layers to match a resolution of
250m x 250m. We performed processing and manipulation of data as well as all
spatial and statistical analyses using R, version 3.6.1 \citep{R.2019}.

@@

%------------------------------------------------------------------------------
%  Appendix S6: Random Effects Variability
%------------------------------------------------------------------------------
\newpage
\section{Habitat Selection Model: Random Effects}
\begin{figure}[hbtp]
  \includegraphics[width = \textwidth]{99_RandomEffects}
  \caption{Plot of random effects showing variability across dispersal
  coalitions.}
  \label{RandomEffects}
\end{figure}

%------------------------------------------------------------------------------
%  Appendix S7: Least Cost Paths and Least Cost Corridors
%------------------------------------------------------------------------------
\newpage
\section{Identification of Least-Cost Paths \& Corridors}
\subsection{Least-Cost Paths}
We implemented factorial LCP analysis between source points using the R-package
\textit{gdistance} (Figure S.7; \citealp{vanEtten.2017}). The package translated
the (unscaled) permeability surface into a network of nodes to find shortest
effective distances between source points based on probabilities of moving from
cell to cell. In our case, the transition probability of moving between two
adjacent cells depended on their averaged permeability. We allowed individuals
to move from each cell to the cell's eight surrounding neighbors (i.e. Moores
neighborhood) and applied a geographic correction to account for the fact that
diagonal neighbors were more remote than orthogonal neighbors. Because African
wild dogs have been observed to cover large dispersal distances
\citep{DaviesMostert.2012, Masenga.2016, Cozzi.2020}, we did not limit LCPs to a
maximal effective cost. After computation, we tallied overlapping LCPs and
identified high-frequency routes.

@@

%  Appendix S8: AIC Model Selection

@@

          cos(ta) + sl + log(sl) + W + T + DTW + HI + S & 90068.15 & 0.00 & 1.00 & -45017.08 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI & 90071.84 & 3.69 & 0.00 & -45020.92 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + S + DTR & 90071.94 & 3.79 & 0.00 & -45016.97 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + S + P & 90071.94 & 3.79 & 0.00 & -45016.97 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + S + RC & 90073.46 & 5.30 & 0.00 & -45015.73 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + DTR & 90075.66 & 7.50 & 0.00 & -45020.83 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + P & 90075.66 & 7.51 & 0.00 & -45020.83 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + S + DTR + P & 90075.79 & 7.64 & 0.00 & -45016.89 \\
          cos(ta) + sl + log(sl) + W + T + DTW + S & 90076.71 & 8.56 & 0.00 & -45023.36 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + RC & 90076.84 & 8.69 & 0.00 & -45019.42 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + S + DTR + RC & 90077.20 & 9.05 & 0.00 & -45015.60 \\
          cos(ta) + sl + log(sl) + W + T + DTW & 90080.08 & 11.92 & 0.00 & -45027.04 \\
          cos(ta) + sl + log(sl) + W + T + DTW + HI + S + DTR + P + RC & 90080.96 & 12.81 & 0.00 & -45015.48 \\
          cos(ta) + sl + log(sl) + W + T + DTW + DTR & 90082.95 & 14.79 & 0.00 & -45026.47 \\
          cos(ta) + sl + log(sl) + W + T + DTW + P & 90083.31 & 15.16 & 0.00 & -45026.66 \\
          cos(ta) + sl + log(sl) + W + T + HI & 90103.28 & 35.13 & 0.00 & -45038.64 \\
          cos(ta) + sl + log(sl) + W + T & 90109.40 & 41.25 & 0.00 & -45043.70 \\
          cos(ta) + sl + log(sl) + W + T + S & 90110.35 & 42.20 & 0.00 & -45042.17 \\
          cos(ta) + sl + log(sl) + W + T + DTR & 90112.55 & 44.40 & 0.00 & -45043.27 \\
          cos(ta) + sl + log(sl) + W + T + P & 90113.11 & 44.96 & 0.00 & -45043.56 \\
          cos(ta) + sl + log(sl) + W + T + RC & 90113.60 & 45.45 & 0.00 & -45041.80 \\
          cos(ta) + sl + log(sl) + W + DTW & 90118.55 & 50.40 & 0.00 & -45048.28 \\
          cos(ta) + sl + log(sl) + W + HI & 90128.70 & 60.54 & 0.00 & -45053.35 \\
          cos(ta) + sl + log(sl) + W + S & 90132.22 & 64.06 & 0.00 & -45055.11 \\
          cos(ta) + sl + log(sl) + W & 90134.85 & 66.69 & 0.00 & -45058.42 \\
          cos(ta) + sl + log(sl) + W + DTR & 90138.31 & 70.16 & 0.00 & -45058.16 \\
          cos(ta) + sl + log(sl) + W + P & 90138.50 & 70.35 & 0.00 & -45058.25 \\
          cos(ta) + sl + log(sl) + W + RC & 90139.30 & 71.15 & 0.00 & -45056.65 \\
          cos(ta) + sl + log(sl) + S & 90141.98 & 73.83 & 0.00 & -45061.99 \\
          cos(ta) + sl + log(sl) + DTW & 90225.64 & 157.49 & 0.00 & -45103.82 \\
          cos(ta) + sl + log(sl) + T & 90271.73 & 203.58 & 0.00 & -45126.86 \\
          cos(ta) + sl + log(sl) + HI & 90273.18 & 205.02 & 0.00 & -45127.59 \\
          cos(ta) + sl + log(sl) + P & 90285.24 & 217.08 & 0.00 & -45133.62 \\
          cos(ta) + sl + log(sl) + DTR & 90285.33 & 217.18 & 0.00 & -45133.67 \\
          cos(ta) + sl + log(sl) + RC & - & - & - & - \\
          cos(ta) + sl + log(sl) + W + T + DTW + RC & - & - & - & - \\

@@

         Road Crossing, DTR = Distance To Roads. The two models at the bottom
         failed to converge, which is why no AIC value could be obtained.
